### 2020-04-14 README.Rmd
Started adjusting the make_html function and generating some figures to start experiments with output.

``` r
# install.packages("devtools")
devtools::install_github("haddonm/aMSE")
devtools::install_github(haddonm/rutilsMH) # also useful for plotting, etc
```
## Example

>>>>

``` r
# install.packages("devtools")
devtools::install_github("haddonm/aMSE")
devtools::install_github(haddonm/rutilsMH) # also useful for plotting, etc
```

Alternatively, you can generate a branch that you can work on by cloning the repository, which, again, can be done very simply within RStudio. Open the New Project option in the project dialog at the top right of the RStudio screen and selection Version Control, then use 'https://github.com/haddonm/aMSE' in the top box, identify where you want the new directory put, and press return.

It would be a good idea to read Hadley Wickham's draft chpater on Git and GitHub at https://r-pkgs.org/index.html.

## Example
